\chapter*{Committees}\rhead{Committees}
%\addstarredchapter{Committees}
%\chaptermark{Committees}
\addcontentsline{toc}{chapter}{Committees} \mtcaddchapter
\vspace{-5em}

\section*{Scientific Committee}\vspace{-1em}
%\addcontentsline{toc}{section}{Scientific Committee} 
\begin{itemize}
\item Prof. David Le Touz\'e (Ecole Centrale de Nantes, France)
\item Dr. Damien Violeau (Electricit\'e de France, France)
\item Dr. Nathan Quinlan (National Univ. of Ireland, Ireland)
\item Dr. Ben Rogers (University of Manchester, UK)
\item Prof. Stefano Sibilla (University of Pavia, Italy)
\item Dr. Jean-Christophe Marongiu (ANDRITZ Hydro, France)
\item Dr. Alex Crespo (Universidade de Vigo, Spain)
\item Dr. Andrea Colagrossi (INSEAN, Italy)
\item Dr. Xiangyu Hu (Technical University of Munich, Germany)
\item Prof. Rade Vignjevic (Brunel University of London, UK)
\item Prof. Thomas Rung (Technical University of Hamburg-Harburg, Germany)
\item Dr. Antonio Souto-Iglesias (Technical University of Madrid, Spain)
\item Dr. Renato Vacondio (University of Parma, Italy)
\item Dr. Matthieu De Leffe (Nextflow Software, France)
\item Prof. Moncho G\'omez-Gesteira (Universidade de Vigo, Spain)
\item Dr. Abbas Khayyer (University of Kyoto, Japan)
\item Prof. Walter Dehnen (University of Leicester, UK)
\item Dr. Raj Das (University of Auckland, New Zealand)
\item Prof. Robert A. Dalrymple (Johns Hopkins University , USA)
\item Prof. Alexis H\'erault (Conservatoire National des Arts et M\'etiers, France)
\item Prof. Joe Monaghan (Monash University, Australia)
\item Prof. Peter Eberhard (University of Stuttgart, Germany)
\item Prof. Moubin Liu (Peking University, China)
\item Dr Mehmet Yildiz (Sabanci University, Turkey)
\end{itemize}



\section*{Organizing Committee}
%\addcontentsline{toc}{section}{Organizing Committee} 
\subsection*{Chair}\vspace{-1em}
\begin{itemize}
\item Prof.   M. B. Liu, Peking University
\end{itemize}

\subsection*{Co-Chairs}\vspace{-1em}
\begin{itemize}
\item Prof.   H. F. Qiang, Xi'an Hi-Tech Institute, China
\item Prof.   A. M. Zhang, Harbin Engineering University, China
\item Prof.   L. Zou, Dalian University of Technology, China
\item Prof.   D. A. Hu, Hunan University, China
\item Prof.   F. Xu, Northwestern Polytechnical University, China
\item Prof.   Z. R. Li, Wenzhou University, China
\end{itemize}



